Attrition in Online Learning: Understanding Persistence and Dropout in Massive Open Online Courses

### 2014-10-30 paper_v1.Rnw

<<loadcsv, echo=FALSE>>=
#library(RCurl)
# data <- getURL("https://raw.githubusercontent.com/whynotyet/MOOC_dropout/master/compiled_data_all_courses.csv", ssl.verifypeer=0L, followlocation=1L)
# a = read.csv(text=data)
a = read.csv("compiled_data_all_courses.csv")

>>>>

<<loadcsv, echo=FALSE, warning=FALSE>>=
library(bitops)
library(RCurl)
data <- getURL("https://raw.githubusercontent.com/whynotyet/MOOC_dropout/master/compiled_data_all_courses.csv", ssl.verifypeer=0L, followlocation=1L)
a = read.csv(text=data)
